Aligning marine species range data to better serve science and conservation

### 2016-02-01 manuscript-main.Rmd

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) 
### NOTE: as of Jan 31, includes all map pairs, even ones where IUCN area == 0

>>>>

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE)
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) 
### NOTE: as of Jan 31, includes all map pairs, even ones where IUCN area == 0
